---
title: "Data Processing"
author: "Vichearith"
date: "11/27/2021"
output: 
  html_document:
    number_sections: true

---

```{r setup, include=FALSE}
knitr::opts_chunk$set(warning=FALSE, message=FALSE, 
                      eval = FALSE, 
                      fig.height = 4, fig.width = 7,
                      fig.align = 'center', fig.pos = 'H')
```

# Load Package

```{r message=FALSE, warning=FALSE}
# Load packages
library(tidyverse)
library(janitor)
library(here)
library(rstan)
library(bayesrules)
library(broom.mixed)
library(tidybayes)
library(bayesplot)
library(rstanarm)
library(forcats)
library(sf)
library(openxlsx)
library(nycgeo)
library(tidycensus)
# themes
theme_set(theme_minimal())
```

# Load Data

## Census Data for Tidycensus package and Cleaning

```{r}
# Get list of county in NYC using `library(nycgeo)`
nyc_join <- merge(nta_sf,nta_acs_data)
nyc_join <- nyc_join %>%
  st_transform(., 4269)
county_list <- nyc_join %>% pull(county_name) %>% unique()

# Fetch census data from `tidycensus` package 
census_api_key("0cc07f06386e317f312adef5e0892b0d002b7254")
census_data <- get_acs(state = "NY", 
        county = c(county_list), 
        geography = "tract", 
        variables = c(medincome = "B19013_001", 
                      total_pop1 = "B01003_001",
                      below_poverty_100 = "B06012_002", 
                      below_poverty_100to150 = "B06012_003",
                      median_rent = "B25031_001", 
                      hholds_snap = "B22003_002", 
                      hholds_disability ="B22010_003",
                      unemployed = "B23025_005", 
                      latinx = "B03002_012", 
                      white = "B03002_003", 
                      black = "B03002_004", 
                      native = "B03002_005",
                      asian = "B03002_006",
                      under19_noinsurance = "B27010_017",
                      age19_34_noinsurance = "B27010_033",
                      age35_64_noinsurance = "B27010_050",
                      age65plus_noinsurance = "B27010_066",
                      naturalized_citizen = "B05001_005",
                      noncitizen ="B05001_006"),
        year = 2019,
        output = "wide",
        survey = "acs5",
        geometry = TRUE) %>% 
  dplyr::select(-c(NAME, ends_with("M"))) %>%
         rename_at(vars(ends_with("E")), .funs = list(~str_sub(., end = -2)))

#  Get mapping of GEOID <--> NTACODE(nta_id)
nta_to_census <- openxlsx::read.xlsx(here("ethnic", "Data", "census_to_nta.xlsx")) %>%
  dplyr::select(GEOID, NTACode)

census_nta <- census_data %>%
  merge(., nta_to_census) %>% # add column : NTACode or (nta_id) 
  mutate(uninsured = under19_noinsurance + age19_34_noinsurance + age35_64_noinsurance + age65plus_noinsurance) %>% # combine all noinsurance of all ages
  dplyr::select(-c(under19_noinsurance, age19_34_noinsurance, age35_64_noinsurance, age65plus_noinsurance)) %>% # remove those unused column
  mutate(NTACode = as.character(NTACode),
         NTACode = ifelse(is.na(NTACode), "NA", NTACode)) %>%
  group_by(NTACode) %>%
  summarize(geometry = st_union(geometry),
            total_pop = sum(total_pop1),
            mean_income = mean(medincome, na.rm = TRUE),
            below_poverty_line_count = sum(below_poverty_100),
            below_poverty_line_and_50_count = sum(below_poverty_100to150),
            mean_rent = mean(median_rent, na.rm = TRUE),
            unemployment_count = sum(unemployed),
            latinx_count = sum(latinx),
            white_count = sum(white),
            black_count = sum(black),
            native_count = sum(native),
            asian_count = sum(asian),
            naturalized_citizen_count = sum(naturalized_citizen),
            noncitizen_count = sum(noncitizen),
            uninsured_count = sum(uninsured))  %>%   # combine data to to get one row per NTAcode
  filter(total_pop != 0) %>% 
  mutate(below_poverty_line_count = below_poverty_line_count/total_pop,
       below_poverty_line_and_50_count = below_poverty_line_and_50_count/total_pop,
       unemployment_count = unemployment_count/total_pop,
       latinx_count = latinx_count/total_pop,
       white_count = white_count/total_pop,
       black_count = black_count/total_pop,
       native_count = native_count/total_pop,
       asian_count = asian_count/total_pop,
       naturalized_citizen_count = naturalized_citizen_count/total_pop,
       noncitizen_count = noncitizen_count/total_pop,
       uninsured_count = uninsured_count/total_pop) %>%
      dplyr::rename(nta_id = NTACode)

names(census_nta) <- gsub(names(census_nta), pattern = "_count", replacement = "_percent")
```

## Other Demographic data

### Grocery

```{r message=FALSE, warning=FALSE}
grocery <- read_csv(here("ethnic","Data","grocery.csv")) %>%
  drop_na(Georeference) %>%
  separate(Georeference, into=c("Point", "longitude", "latitude"), " ") %>%
  mutate(latitude = str_remove_all(latitude, "[)]"),
         longitude = str_remove_all(longitude, "[()]"),
         ) %>%
  dplyr::select(-c(Point)) %>% 
  mutate(latitude = as.numeric(latitude),
         longitude = as.numeric(longitude)) %>%
  st_as_sf(coords = c("longitude", "latitude"), crs = 4269)
```

### Public School

```{r message=FALSE, warning=FALSE}
public_schools <- st_read(here("ethnic","Data","schools", "Public_Schools_Points_2011-2012A.shp")) %>%
  st_transform(., 4269)
```

### Subway Station
```{r message=FALSE, warning=FALSE}
subway_stations <- st_read(here("ethnic","Data","stations", "geo_export_85568705-efba-4456-bdc0-3d70ff2cf8e5.shp")) %>%
  st_transform(., 4269)
```
### Bus Station

```{r message=FALSE, warning=FALSE}
bus_stations <- st_read(here("ethnic","Data","bus", "bus_stops_nyc_may2020.shp")) %>%
  st_transform(., 4269)

```

### Eviction
```{r message=FALSE, warning=FALSE}
evictions <- read_csv(here("ethnic","Data","evictions.csv")) %>%
  drop_na(Longitude) %>%
  drop_na(Latitude) %>%
  st_as_sf(coords = c("Longitude", "Latitude"), crs = 4269)
```
### Transit 

```{r}
transit_points <- read_csv(here("transit","ridership_points.csv"))%>%
  separate(Position, into=c("Point", "longitude", "latitude"), " ") %>%
  mutate(latitude = str_remove_all(latitude, "[)]"),
         longitude = str_remove_all(longitude, "[()]"),
         ) %>%
  dplyr::select(-c(Point)) %>% 
  mutate(latitude = as.numeric(latitude),
         longitude = as.numeric(longitude)) %>%
  st_as_sf(coords = c("longitude", "latitude"), crs = 4269)

```
### Transit Area
```{r}
transit_area <- read_csv("transit/Summarize234_Buffer_of_transit_shps_within_NYC_Neighborhood_Tabulation_Areas_2020_0.csv") %>%
  mutate(perc_covered_by_transit = (`Summarized Area in Square Miles`/`Area in Square Miles`)*100) %>%
  dplyr::select(NTA2020, perc_covered_by_transit) %>%
  dplyr::rename(nta_id= NTA2020)
```
### NTA IDs and Names
```{r}
nta_info <- read_csv(here("demographics","demographics.csv")) %>%
  rename(census_tract = BCT2020) %>%
  drop_na(`NTA Type`) %>%
  #select(`NTA Type`, GeoID, Name) %>%
  filter(!substr(GeoID, 1, 2) == "SI") %>%
  rename(nta_id = GeoID) %>%
  rename(nta_type = `NTA Type`) %>% 
  dplyr::select(nta_type, nta_id, Name)
```


# Join Data
## Combine All Other Demographic data 
```{r}
nyc_schools_join <- st_join(census_nta, public_schools) %>%
  group_by(nta_id) %>%
  summarize(school_count=n())

nyc_grocery_join <- st_join(census_nta, grocery) %>%
  group_by(nta_id) %>%
  summarize(store_count=n())

nyc_evictions_join <- st_join(census_nta, evictions)%>%
  group_by(nta_id) %>%
  summarize(eviction_count=n())

nyc_stop_join <- st_join(census_nta, subway_stations)%>%
  group_by(nta_id) %>%
  summarize(sub_count=n())

nyc_bus_stop_join <- st_join(census_nta, bus_stations)%>%
  group_by(nta_id) %>%
  summarize(bus_count=n())

nyc_ridership_join <- st_join(census_nta, transit_points) %>%
  group_by(nta_id) %>%
  summarize(mean_ridership = mean(`2018Ridership`))

#everything is a tibble, dplyr join commands by nta. st_as_sf to convert to shapefiles

Other_demographic_combined <- as.data.frame(nyc_schools_join) %>%
  full_join(., (as.data.frame(nyc_evictions_join)), by= "nta_id") %>%
  full_join(., (as.data.frame(nyc_grocery_join)), by= "nta_id") %>%
  full_join(., (as.data.frame(nyc_stop_join)), by= "nta_id") %>%
  full_join(., (as.data.frame(nyc_bus_stop_join)), by= "nta_id") %>%
  full_join(., (as.data.frame(nyc_ridership_join)), by= "nta_id") %>%
  dplyr::select(-c(geometry.x, geometry.y, geometry.x.x, geometry.y.y, geometry.x.x.x, geometry.y.y.y))
```

## Merge Other Demographic Combination with Census Data By NTA
```{r}
## Original Code:-------------------------------------
# nyc_compiled <- merge(census_nta, data, by = "nta_id")
#
# nyc_compiled2 <- left_join(nyc_compiled, transit_area, by="nta_id" ) 
# 
# 
# nyc_compiled2 %>%
#   write_csv(., "clean_data/nyc_names.csv") %>%
#   write_sf(., "clean_data/nyc_data.shp")
## ----------------------------------------------------
#       ^
#       |
#       |

#  Merge All other demographic data with census_nta by nta_id
clean_data <- merge(census_nta, Other_demographic_combined, by = "nta_id")
```

## Add Coverage by Transit for Each NTA

```{r}
clean_data<- clean_data %>% 
  left_join( transit_area, by="nta_id" )
```

## Add NTA Name

```{r}
# add NTA Name and NTA type by nta_id
clean_data <- clean_data %>% 
   merge(nta_info, by="nta_id")
```

## Filter Staten Island 

```{r}
# Filter out Staten Island
clean_data <- clean_data %>%
  filter(!substr(nta_id, 1, 2) == "SI")
```

## Add Subway Desert Categorical Variable 

```{r}
clean_data <- clean_data %>%
  mutate(transportation_desert_4cat = cut(perc_covered_by_transit, breaks=c(-1, 10, 75, 99, 100), labels = c("1", "2", "3", "4"))) %>% 
  relocate( geometry, .after = last_col())
```

# Write Final Data to File
```{r}
# write to file
clean_data %>% 
  write_csv(., "clean_data/nyc_names_vichy_complied.csv") %>%
  write_sf(., "clean_data/nyc_data_vichy_complied.shp")
```
# Reading Complied Data 
```{r}
#  Read CSV File
csv_file_clean <- read_csv("clean_data/nyc_names.csv")
#  Read Shape File
shape_file_clean <- st_read("clean_data/nyc_data.shp", crs = 4269)
#  Replace Column abbr Names in Shape File with full name from CSV
colnames(shape_file_clean) <- colnames(csv_file_clean)

# Verify
names(shape_file_clean)
names(csv_file_clean)


```





