---
title: "juthi_second"
author: "Juthi Dewan"
date: "11/30/2021"
output: html_document
---


```{r setup, include=FALSE}
knitr::opts_chunk$set(warning=FALSE, message=FALSE, 
                      fig.height = 4, fig.width = 7,
                      fig.align = 'center', fig.pos = 'H')

```

```{r}
# Load packages
library(tidyverse)
library(janitor)
library(here)
library(rstan)
library(rstanarm)
library(bayesrules)
library(tidyverse)
library(rstanarm)
library(broom.mixed)
library(tidybayes)
library(bayesplot)
library(bayesrules)
library(tidyverse)
library(rstanarm)
library(broom.mixed)
library(tidybayes)
library(forcats)
library(bayesplot)
library(sf)
# themes
theme_set(theme_minimal())
```


```{r}
# Load packages
library(here)
library(dplyr)
library(readr)
library(rstan)
library(bayesrules)
library(tidyverse)
library(bayesplot)
library(rstanarm)
library(janitor)
library(tidybayes)
library(broom.mixed)
library(here)
library(sf)
library(tidycensus)
library(openxlsx)
library(s2)
library(nycgeo)
library(CARBayes)
library(spData) 
library(spdep)

nyc_join <- merge(nta_sf,nta_acs_data)


nyc_join <- nyc_join %>%
  st_transform(., 4269)

county_list <- nyc_join %>% pull(county_name) %>% unique()


census_api_key("0cc07f06386e317f312adef5e0892b0d002b7254")

census_data <- get_acs(state = "NY", 
        county = c(county_list), 
        geography = "tract", 
        variables = c(gini_inequality ="B19083_001"),
        year = 2019,
        output = "wide",
        survey = "acs5",
        geometry = TRUE) %>% 
  dplyr::select(-c(NAME, ends_with("M"))) %>%
         rename_at(vars(ends_with("E")), .funs = list(~str_sub(., end = -2)))  %>%
  st_transform(., 4269) %>%
  dplyr::select(-GEOID)
```


```{r}
vari_names <- read_csv("clean_data/nyc_names_vichy_complied.csv")
nyc_clean <- st_read("clean_data/nyc_data_vichy_complied.shp")
colnames(nyc_clean) <- colnames(vari_names)
```


```{r}
gini_neighborhood <- st_join(nyc_clean, census_data,left = TRUE) %>%
  group_by(nta_id) %>%
  summarize(gini_neighborhood=median(gini_inequality, na.rm=T)) %>%
  as.tibble() %>%
  dplyr::select(nta_id, gini_neighborhood) 

nyc_clean <- nyc_clean %>%
  as.tibble() %>%
  # filter(nta_id %in% sex_assault_gini$nta_id) %>%
  left_join(., gini_neighborhood, by="nta_id")%>% 
  unique() %>%
  st_as_sf()
```


For the part of the project we are exploring the variable noncitizen_count. This is a variable of interest because we want to see what drives the number of citizens in a neighborhood. 

```{r}
nyc_perc <- nyc_clean %>%
   mutate(asian_perc = asian_count / total_pop) %>%
   mutate(white_perc = white_count / total_pop) %>%
   mutate(black_perc = black_count / total_pop) %>%
   mutate(latinx_perc = latinx_count / total_pop) %>%
   mutate(native_perc = native_count / total_pop) %>%
   mutate(noncitizen_perc = noncitizen_count / total_pop) %>%
   mutate(evictions_perc = eviction_count / total_pop) %>%
   mutate(uninsured_perc = uninsured_count / total_pop) %>%
  mutate(unemployment_perc = unemployment_count / total_pop)

nyc_compiled <- nyc_perc %>%
  filter(nta_type == "0")
```

```{r}
#mapping non-citizen percentage in NYC residential neighborhoods
ggplot(nyc_compiled) +
  geom_sf(aes(fill = noncitizen_count), color = "#8f98aa") +
  scale_fill_gradient(low = "#FCF5EE", high = "#717EC3", guide = guide_legend(title = "Percent Non-Citizen")) +
  theme_minimal() +
  theme(panel.grid.major = element_line("transparent"),
        axis.text = element_blank()) +
  ggtitle("Non Citizen Percentage in NYC Residential Neighborhoods")+ 
    theme(panel.grid.major = element_line("transparent"),
          plot.title = element_text(size = 15, face = "bold"),
          legend.title = element_text(size = 8), 
          legend.text = element_text(size = 8)) + 
    guides(shape = guide_legend(override.aes = list(size = 4)),
           color = guide_legend(override.aes = list(size = 4)))


#mapping non-citizen percentage in every NYC neighborhood
ggplot(nyc_compiled) +
  geom_sf(aes(fill = noncitizen_perc), color = "#8f98aa") +
  scale_fill_gradient(low = "#FCF5EE", high = "#717EC3", guide = guide_legend(title = "Percent Non-Citizen")) +
  theme_minimal() +
  theme(panel.grid.major = element_line("transparent"),
        axis.text = element_blank()) +
  ggtitle("Non Citizen Percentage in all of NYC")+ 
    theme(panel.grid.major = element_line("transparent"),
          plot.title = element_text(size = 15, face = "bold"),
          legend.title = element_text(size = 8), 
          legend.text = element_text(size = 8)) + 
    guides(shape = guide_legend(override.aes = list(size = 4)),
           color = guide_legend(override.aes = list(size = 4)))

```


```{r}
nyc_compiled %>%
ggplot(aes(x = noncitizen_perc)) +
  geom_density(alpha = 0.7, fill = "blue") +
  facet_wrap("transportation_desert_4cat") 
  theme_minimal() +
   theme(panel.grid.major = element_line("transparent"),
        axis.text = element_blank())
```

This plot above tells us a little bit about non citizen percentage and public transit access. This isn't all that much informative, but it's still interesting to see how the non citizen percentage changes with different accessibility categories. 





```{r}
#modeling a negative binomial model for the number of non-citizens 
non_citizen_model <- stan_glm(
  noncitizen_count ~
  transportation_desert_4cat + 
  total_pop + borough + gini_neighborhood + mean_income + mean_rent + unemployment_perc + 
  black_perc + latinx_perc + asian_perc,
  data = nyc_compiled,
  family = neg_binomial_2,
  chains = 2, iter = 1000*2, seed = 84735, refresh = 0
)

pp_check(non_citizen_model)

tidy(non_citizen_model, effects = "fixed", conf.int = TRUE, conf.level = 0.8)

prediction_summary_cv(model = non_citizen_model, data=nyc_compiled, k=10)$cv
```


```{r}
non_citizen_clean <- nyc_compiled %>%
  na.omit()%>%
  arrange(noncitizen_count)

list <- non_citizen_clean %>%
  arrange(noncitizen_count) %>% pull(noncitizen_count)


set.seed(84735)

predictions_non_citizen <-  posterior_predict(
  non_citizen_model, newdata = non_citizen_clean)

ppc_intervals(list, yrep = predictions_non_citizen,
              prob_outer = 0.8) +
  ggplot2::scale_x_continuous(
    labels = non_citizen_clean$nta_id,
    breaks = 1:nrow(non_citizen_clean)) +
	xaxis_text(angle = 90,  hjust = 1) +
  theme_linedraw()+
  theme(panel.grid.major = element_line("transparent"),
        axis.title.x = element_blank(),
        axis.text.x = element_blank())

library(kableExtra)
tidy(non_citizen_model, effects = "fixed", conf.int = TRUE, conf.level = 0.8)%>% 
  
  mutate(estimate= ifelse(term == "(Intercept)", exp(estimate), (exp(estimate)-1)*100), 
         conf.low= ifelse(term == "(Intercept)", exp(conf.low), (exp(conf.low)-1)*100), 
         conf.high = ifelse(term == "(Intercept)", exp(conf.high), (exp(conf.high)-1)*100))%>%
  filter(conf.low	> 0 & conf.high > 0 | conf.low	< 0 & conf.high < 0) %>%
  kable(align = "c", caption = "Non Citizen Negative Binomial - Model Summary") %>% 
  kable_styling()
```



```{r}
rent_model <- stan_glm(
mean_rent  ~ 
  transportation_desert_4cat + bus_count + school_count + store_count +
  total_pop + borough + gini_neighborhood + mean_income + noncitizen_perc +
  black_perc + latinx_perc + asian_perc,
  data = nyc_compiled, 
  family = gaussian,
 prior_intercept = normal(1580 , 20),
  chains = 2, iter = 1000*2, seed = 84735, refresh = 0
)

pp_check(rent_model)

tidy(rent_model, effects = "fixed", conf.int = TRUE, conf.level = 0.8)

prediction_summary_cv(model = rent_model, data=nyc_compiled, k=10)$cv
```

We thought it would be interesting to look at mean rent and looking at some of the significant explanatory variables. The model above, so much is significant!! kind of crazy 



```{r}
rent_clean <- nyc_compiled %>%
  na.omit()%>%
  arrange(mean_rent)

list <- rent_clean %>%
  arrange(mean_rent) %>% pull(mean_rent)


set.seed(84735)

predictions_mean_rent <-  posterior_predict(
  rent_model, newdata = rent_clean)

ppc_intervals(list, yrep = predictions_mean_rent,
              prob_outer = 0.8) +
  ggplot2::scale_x_continuous(
    labels = rent_clean$nta_id,
    breaks = 1:nrow(rent_clean)) +
	xaxis_text(angle = 90,  hjust = 1) +
  theme_linedraw()+
  theme(panel.grid.major = element_line("transparent"),
        axis.title.x = element_blank(),
        axis.text.x = element_blank())

library(kableExtra)
tidy(rent_model, effects = "fixed", conf.int = TRUE, conf.level = 0.8)%>% 
  
  mutate(estimate= ifelse(term == "(Intercept)", exp(estimate), (exp(estimate)-1)*100), 
         conf.low= ifelse(term == "(Intercept)", exp(conf.low), (exp(conf.low)-1)*100), 
         conf.high = ifelse(term == "(Intercept)", exp(conf.high), (exp(conf.high)-1)*100))%>%
  filter(conf.low	> 0 & conf.high > 0 | conf.low	< 0 & conf.high < 0) %>%
  kable(align = "c", caption = "Rent Normal Distribution - Model Summary") %>% 
  kable_styling()
```


```{r}
eviction_model <- stan_glm(
eviction_count  ~ 
  transportation_desert_4cat +
  total_pop + borough + 
  gini_neighborhood + mean_income + unemployment_perc +  mean_rent + 
  bus_count +
  black_perc + latinx_perc + asian_perc,
  data = nyc_compiled, 
  family = neg_binomial_2,
  chains = 2, iter = 1000*2, seed = 84735, refresh = 0
)

pp_check(eviction_model)

tidy(eviction_model, effects = "fixed", conf.int = TRUE, conf.level = 0.8)

prediction_summary_cv(model = eviction_model, data=nyc_compiled, k=10)$cv
```

```{r}
manhattan <- nyc_compiled %>%
  filter(borough == "Manhattan")

queens <- nyc_compiled %>%
  filter(borough == "Queens")

bronx <- nyc_compiled %>%
  filter(borough == "Bronx")

brooklyn <- nyc_compiled %>%
  filter(borough == "Brooklyn")
```

```{r}
#mapping non-citizen percentage in NYC residential neighborhoods
ggplot(manhattan) +
  geom_sf(aes(fill = noncitizen_perc), color = "#8f98aa") +
  scale_fill_gradient(low = "#FCF5EE", high = "#717EC3", guide = guide_legend(title = "Percent Non-Citizen")) +
  theme_minimal() +
  theme(panel.grid.major = element_line("transparent"),
        axis.text = element_blank()) +
  ggtitle("Non Citizen Percentage in Manhattan")+ 
    theme(panel.grid.major = element_line("transparent"),
          plot.title = element_text(size = 15, face = "bold"),
          legend.title = element_text(size = 8), 
          legend.text = element_text(size = 8)) + 
    guides(shape = guide_legend(override.aes = list(size = 4)),
           color = guide_legend(override.aes = list(size = 4)))


ggplot(brooklyn) +
  geom_sf(aes(fill = noncitizen_perc), color = "#8f98aa") +
  scale_fill_gradient(low = "#FCF5EE", high = "#717EC3", guide = guide_legend(title = "Percent Non-Citizen")) +
  theme_minimal() +
  theme(panel.grid.major = element_line("transparent"),
        axis.text = element_blank()) +
  ggtitle("Non Citizen Percentage in Brooklyn")+ 
    theme(panel.grid.major = element_line("transparent"),
          plot.title = element_text(size = 15, face = "bold"),
          legend.title = element_text(size = 8), 
          legend.text = element_text(size = 8)) + 
    guides(shape = guide_legend(override.aes = list(size = 4)),
           color = guide_legend(override.aes = list(size = 4)))

ggplot(queens) +
  geom_sf(aes(fill = noncitizen_perc), color = "#8f98aa") +
  scale_fill_gradient(low = "#FCF5EE", high = "#717EC3", guide = guide_legend(title = "Percent Non-Citizen")) +
  theme_minimal() +
  theme(panel.grid.major = element_line("transparent"),
        axis.text = element_blank()) +
  ggtitle("Non Citizen Percentage in Queens")+ 
    theme(panel.grid.major = element_line("transparent"),
          plot.title = element_text(size = 15, face = "bold"),
          legend.title = element_text(size = 8), 
          legend.text = element_text(size = 8)) + 
    guides(shape = guide_legend(override.aes = list(size = 4)),
           color = guide_legend(override.aes = list(size = 4)))

ggplot(bronx) +
  geom_sf(aes(fill = noncitizen_perc), color = "#8f98aa") +
  scale_fill_gradient(low = "#FCF5EE", high = "#717EC3", guide = guide_legend(title = "Percent Non-Citizen")) +
  theme_minimal() +
  theme(panel.grid.major = element_line("transparent"),
        axis.text = element_blank()) +
  ggtitle("Non Citizen Percentage in Bronx")+ 
    theme(panel.grid.major = element_line("transparent"),
          plot.title = element_text(size = 15, face = "bold"),
          legend.title = element_text(size = 8), 
          legend.text = element_text(size = 8)) + 
    guides(shape = guide_legend(override.aes = list(size = 4)),
           color = guide_legend(override.aes = list(size = 4)))
```



```{r}
nyc_compiled %>%
ggplot(aes(x = black_perc)) +
  geom_density(alpha = 0.7, fill = "blue") +
  facet_wrap("borough") 
  theme_minimal() +
   theme(panel.grid.major = element_line("transparent"),
        axis.text = element_blank())
  
  nyc_compiled %>%
ggplot(aes(x = white_perc)) +
  geom_density(alpha = 0.7, fill = "blue") +
  facet_wrap("borough") 
  theme_minimal() +
   theme(panel.grid.major = element_line("transparent"),
        axis.text = element_blank())
  
nyc_compiled %>%
ggplot(aes(x = noncitizen_perc, fill = transportation_desert_4cat)) +
  geom_density(alpha = 0.5) +
  facet_wrap("borough") 
  theme_minimal() +
   theme(panel.grid.major = element_line("transparent"),
        axis.text = element_blank())
 
  #this last graph is a good representation of how the boroughs vary greatly between one another. So, we decided to make hierarchical models and group it by borough to account for the differences between the different boroughs.

viz_rent <- nyc_compiled %>%
ggplot(aes(x = mean_rent, fill = transportation_desert_4cat)) +
  geom_density(alpha = 0.5) +
  facet_wrap("borough") 
  theme_minimal() +
   theme(panel.grid.major = element_line("transparent"),
        axis.text = element_blank())  
  
viz_income <- nyc_compiled %>%
ggplot(aes(x = mean_income, fill = transportation_desert_4cat)) +
  geom_density(alpha = 0.5) +
  facet_wrap("borough") 
  theme_minimal() +
   theme(panel.grid.major = element_line("transparent"),
        axis.text = element_blank())  
```


