---
title: "OrdinalSectionUpdate"
author: "Sam Ding"
date: "12/10/2021"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

# data intro
```{r}
# Load packages
library(tidyverse)
library(janitor)
library(here)
library(rstan)
library(rstanarm)
library(bayesrules)
library(tidyverse)
library(rstanarm)
library(broom.mixed)
library(tidybayes)
library(bayesplot)
library(bayesrules)
library(forcats)
library(sf)
library(nycgeo)
library(tidycensus)
library(extrafont)
library(extrafontdb)
# themes
theme_set(theme_minimal())
brown_green <- c("#E9DBC2","#7D9B8A","#4D6F5C","#D29B5B","#744410","#1C432D")
color_scheme_set(brown_green)
```
## Ordinal Model

Having realized the shortcomings of the naive Bayes model, we wanted to see if there are any alternatives. We land on the ordinal regression model. 

An ordinal regression model predicts the outcome of an ordinal variable, i.e. a variable whose value exists on an arbitrary scale where only the relative ordering between different values is significant. In this case, our subway desert classification is the ordinal variables with categories ranging from the least covered to the most covered (1 ~ 4)

$$

Y_i| \zeta_1, \zeta_2,\zeta_3,\beta_1, \beta_2,\beta_3, \beta_4 =
\begin{cases}
1 &, y^{*} < \zeta_1 \\
2 &, \zeta_1 \leq y^{*} < \zeta_2 \\
3 &, \zeta_2 \leq y^{*} < \zeta_3 \\
4 &, y^{*} \geq \zeta_3 \\
\end{cases} 

\\
y^{*} = \beta_1x_1 + \beta_2x_2 + \beta_3x_3 + \beta_4x_4 + \epsilon \\

$$
- $\zeta_i$ : is a vector of cut-points for categories. 
- $y^{*}$ : a linear combination of 6 predictor variables consisting of `mean income`, `below poverty percentage`, `eviction count`, and `store_count`.
- $\beta_i$ : is the coefficient for the $ith$ predictor variable. 

$$
\zeta_1 \sim N(m_{\zeta 1}, s_{\zeta 1}^{2}) \\
\zeta_2 \sim N(m_{\zeta 2}, s_{\zeta 2}^{2}) \\
\zeta_3 \sim N(m_{\zeta 3}, s_{\zeta 3}^{2}) \\
\zeta_4 \sim N(m_{\zeta 4}, s_{\zeta 4}^{2}) \\
\beta_1 \sim N(m_{\beta 1}, s_{\beta 1}^{2}) \\
\beta_2 \sim N(m_{\beta 2}, s_{\beta 2}^{2}) \\
\beta_3 \sim N(m_{\beta 3}, s_{\beta 3}^{2}) \\
\beta_4 \sim N(m_{\beta 4}, s_{\beta 4}^{2}) \\
$$
Since we do not have prior information about the data, we will be using the default prior R2 given by the `stan_polr` function. 

Note:
- There is no intercept in this model because the data cannot distinguish an intercept from the cut points. 


```{r}
library(rsample)
set.seed(454)

nyc_compiled_classify <- nyc_compiled %>%
  mutate(transportation_desert_4cat = factor(transportation_desert_4cat, levels=c("Poor", "Limited", "Satisfactory", "Excellent"))) %>%
  mutate(transportation_desert_4num = factor(as.numeric(transportation_desert_4cat))) %>%
   mutate(asian_perc = (asian_count / total_pop) * 100) %>%
   mutate(white_perc = (white_count / total_pop)* 100) %>%
   mutate(black_perc = (black_count / total_pop)* 100) %>%
   mutate(latinx_perc = (latinx_count / total_pop)* 100) %>%
   mutate(native_perc = (native_count / total_pop)* 100) %>%
   mutate(below_poverty_perc = (below_poverty_line_count / total_pop) * 100) %>%
   mutate(noncitizen_perc = (noncitizen_count / total_pop)* 100) %>%
   mutate(uninsured_perc = (uninsured_count / total_pop)* 100) %>%
  mutate(unemployment_perc = (unemployment_count / total_pop)* 100) %>%
  filter(nta_type == 0) %>%
  as.tibble()

data_split <- initial_split(nyc_compiled_classify, prop = .8) 
data_train <- training(data_split)
data_test <- testing(data_split) 
```

```{r}
model2 <- stan_polr(as.factor(transportation_desert_4num) ~ mean_income + below_poverty_line_perc + store_count, 
                    data =data_train, prior_counts = dirichlet(1),
                    prior=R2(0.5), iter=500, seed = 86437, refresh=0, prior_PD=FALSE)


tidy(model2, effects = "fixed", conf.int = TRUE, conf.level = 0.8) %>%
  mutate(term = case_when(
    term == "1|2" ~ "Poor | Limited",
    term == "2|3" ~ "Limited | Satisfactory",
    term == "3|4" ~ "Satisfactory | Excellent",
    TRUE ~ term
    ))%>%
  kable(align = "c", caption = "Ordinal Model - Summary") %>% 
  kable_styling() 
```

Then using a function written by [Connie Zhang](https://connie-zhang.github.io/pet-adoption/modelling.html), we describe the accuracy of the ordinal model below.

```{r}
ordinal_accuracy<-function(post_preds,mydata){
  post_preds<-as.data.frame(post_preds)
  results<-c()
  for (j in (1:length(post_preds))){
    results[j]<-as.numeric(tail(names(sort(table(post_preds[,j]))))[4])
    }
  results<-as.data.frame(results)
  compare<-cbind(results,mydata$transportation_desert_4num)
  compare<-compare %>%mutate(results=as.numeric(results))
  compare<-compare %>% mutate(`mydata$transportation_desert_4num`=as.numeric(`mydata$transportation_desert_4num`))
  compare<-compare %>%mutate(accuracy=ifelse(as.numeric(results)==as.numeric(`mydata$transportation_desert_4num`),1,0))
  print(sum(compare$accuracy)/length(post_preds))
}
```




```{r}
nyc_compiled[is.na(nyc_compiled)] = 0

set.seed(86437)

my_prediction2 <- posterior_predict(
  model2, 
  newdata = data_test)

ordinal_accuracy(my_prediction2, data_test)
```


```{r}
my_prediction2 <- posterior_predict(
  model2, 
  newdata = data_test)

prediction_long <- my_prediction2 %>% 
  t() %>% 
  as.tibble() %>%
  mutate_if(is.character, as.numeric) %>%
  rownames_to_column() %>% 
  rowwise(id=rowname) %>%
  summarize(median=ifelse(mean(c_across(where(is.numeric)))>3.5, ceiling(mean(c_across(where(is.numeric)))), floor(mean(c_across(where(is.numeric)))))) %>%
  rename(predicted_desert = median)%>%
  mutate(predicted_desert = case_when(
    predicted_desert==1 ~ "Poor",
    predicted_desert ==2 ~ "Limited",
    predicted_desert ==3 ~ "Satisfactory",
    TRUE ~ "Excellent",
  ))  %>%
  mutate(predicted_desert = factor(predicted_desert, levels=c("Poor", "Limited", "Satisfactory", "Excellent")))

data_test %>%
  dplyr::select(nta_id, borough, transportation_desert_4cat) %>%
  rownames_to_column() %>%
  left_join(., prediction_long, by="rowname") %>%
  
  ggplot(aes(x=transportation_desert_4cat, fill=predicted_desert)) + 
  geom_bar(position="fill")+
  scale_y_continuous(labels = seq(0, 100, by = 25)) +
  labs(title="Accessibility Predictions by Observed Category", y="Proportion", x="")+
    theme(panel.grid.major.x = element_line("transparent"),
         # axis.text.y.left = element_blank(),
          axis.text.x.bottom = element_text(size = 12, face = "bold"),
          plot.title = element_text(family="DIN Condensed", size =20, hjust=.5, face = "bold")) +
   scale_fill_manual(values=c("#895F32","#E9DBC2","#7D9B8A", "#395645"),
                       guide = guide_legend(title = "Subway Accessibility \nCategory"), na.value="#D6D6D6")
  