---
title: "STAT 454: Capstone 3"
author: Freddy Barragan, Juthi Dewan, Sam Ding, Vichy Meas
date: "`r format(Sys.time(), '%d %B, %Y')`"
output: 
  html_document:
    toc: true
    toc_float: true
    code_folding: hide
---

<style>
.list-group-item.active, .list-group-item.active:focus, .list-group-item.active:hover {
z-index: 2;
color: #FFFFFF;
background-color: #000000;
border-color: #000000;
}
</style>


```{r setup, include=FALSE}
knitr::opts_chunk$set(warning=FALSE, message=FALSE, 
                      fig.height = 4, fig.width = 7,
                      fig.align = 'center', fig.pos = 'H')
```


```{r}
# Load packages
library(here)
library(dplyr)
library(readr)
library(rstan)
library(bayesrules)
library(tidyverse)
library(bayesplot)
library(rstanarm)
library(janitor)
library(tidybayes)
library(broom.mixed)
library(here)
library(sf)
library(tidycensus)
library(openxlsx)
library(s2)
```


```{r}
# themes
theme_set(theme_minimal())
vari_names <- read_csv(here("clean_data", "nyc_names.csv"))
nyc_clean <- st_read(here("clean_data", "nyc_data.shp"), crs = 4269) 
colnames(nyc_clean) <- colnames(vari_names)


library(openxlsx)
nta_to_census <- openxlsx::read.xlsx(here("ethnic", "Data", "census_to_nta.xlsx")) %>%
  dplyr::select(BoroName, NTACode) %>%
  rename(borough = BoroName,
         nta_id = NTACode) %>%
  unique()

nyc_clean <- nyc_clean %>%
  merge(., nta_to_census, by="nta_id") %>%
  mutate(transportation_desert_4cat = factor(transportation_desert_4cat, levels=c("No Access", "Limited Access", "Satisfactory Access", "Excellent Access")))
```

```{r}
subway_stations <- st_read(here("ethnic","Data","stations", "geo_export_85568705-efba-4456-bdc0-3d70ff2cf8e5.shp")) %>%
  st_transform(., 4269)

bus_stations <- st_read(here("ethnic","Data","bus", "bus_stops_nyc_may2020.shp")) %>%
  st_transform(., 4269)

transit_points <- read_csv(here("transit","ridership_points.csv"))%>%
  separate(Position, into=c("Point", "longitude", "latitude"), " ") %>%
  mutate(latitude = str_remove_all(latitude, "[)]"),
         longitude = str_remove_all(longitude, "[()]"),
         ) %>%
  dplyr::select(-c(Point)) %>% 
  mutate(latitude = as.numeric(latitude),
         longitude = as.numeric(longitude)) %>%
  st_as_sf(coords = c("longitude", "latitude"), crs = 4269)
```


```{r, fig.height=5*1.2, fig.width=5*1.2}
#plot locations over map
subway_loc <- ggplot() +
  geom_sf(data = nyc_clean, fill = "#EBF6FF", color = "#D48DD8", size = 0.15, alpha = .8) +
  geom_sf(data = subway_stations, color="#3F123C", size=1) + 
  coord_sf(datum = st_crs(subway_stations)) +
  theme_minimal() +
  theme(panel.grid.major = element_line("transparent"),
        axis.text = element_blank()) +
  ggtitle("Subway Stop Locations \nin NYC")+ 
    theme(#panel.grid.major = element_line("transparent"),
          plot.title = element_text(size = 30, face = "bold"),
          legend.title = element_text(size = 12), 
          legend.text = element_text(size = 12)) + 
    guides(shape = guide_legend(override.aes = list(size = 8)),
           color = guide_legend(override.aes = list(size = 8)))

bus_loc <- ggplot() +
  geom_sf(data = nyc_clean, fill = "#EBF6FF", color = "#D48DD8", size = 0.15, alpha = .8) +
  geom_sf(data = bus_stations, color="#3F123C", size=.5, alpha=.5) + 
  coord_sf(datum = st_crs(subway_stations)) +
  theme_minimal() +
  theme(panel.grid.major = element_line("transparent"),
        axis.text = element_blank()) +
  ggtitle("Bus Stop Locations \nin NYC")+ 
    theme(#panel.grid.major = element_line("transparent"),
          plot.title = element_text(size = 30, face = "bold"),
          legend.title = element_text(size = 12), 
          legend.text = element_text(size = 12)) + 
    guides(shape = guide_legend(override.aes = list(size = 8)),
           color = guide_legend(override.aes = list(size = 8)))


stops <- nyc_clean %>%
  ggplot() +
  geom_sf(aes(fill = sub_count), color = "#8f98aa") +
  scale_fill_gradient(low= "lavender", high = "maroon",
                      guide = guide_legend(title = "Number of Subway Stops") ,na.value="#D6D6D6") +
  theme_minimal() +
  theme(panel.grid.major = element_line("transparent"),
        axis.text = element_blank()) +
  ggtitle("Subway Stop Counts \nin NYC")+ 
    theme(panel.grid.major = element_line("transparent"),
          plot.title = element_text(size = 30, face = "bold"),
          legend.title = element_text(size = 12), 
          legend.text = element_text(size = 12)) + 
    guides(shape = guide_legend(override.aes = list(size = 8)),
           color = guide_legend(override.aes = list(size = 8)))

bus_stops <- nyc_clean %>%
  ggplot() +
  geom_sf(aes(fill = bus_count), color = "#8f98aa") +
  scale_fill_gradient(low= "lavender", high = "maroon",
                      guide = guide_legend(title = "Number of Bus Stops") ,na.value="#D6D6D6") +
  theme_minimal() +
  theme(panel.grid.major = element_line("transparent"),
        axis.text = element_blank()) +
  ggtitle("Bus Stop Counts \nin NYC")+ 
    theme(panel.grid.major = element_line("transparent"),
          plot.title = element_text(size = 30, face = "bold"),
          legend.title = element_text(size = 12), 
          legend.text = element_text(size = 12)) + 
    guides(shape = guide_legend(override.aes = list(size = 8)),
           color = guide_legend(override.aes = list(size = 8)))


ridership <- nyc_clean%>%
  ggplot() +
  geom_sf(aes(fill = log2(mean_ridership)), color = "#8f98aa") +
  scale_fill_gradient(low= "lavender", high = "maroon",
                      guide = guide_legend(title = "Log2 Mean Ridership") ,na.value="#D6D6D6") +
  theme_minimal() +
  theme(panel.grid.major = element_line("transparent"),
        axis.text = element_blank()) +
  ggtitle("Mean (Log2) Subway Turnstile \nRidership in 2018 \nfor NYC")+ 
    theme(panel.grid.major = element_line("transparent"),
          plot.title = element_text(size = 30, face = "bold"),
          legend.title = element_text(size = 12), 
          legend.text = element_text(size = 12)) + 
    guides(shape = guide_legend(override.aes = list(size = 8)),
           color = guide_legend(override.aes = list(size = 8)))

access <- nyc_clean %>%
  ggplot() +
  geom_sf(aes(fill = transportation_desert_4cat), color = "#8f98aa") +
  scale_fill_manual(values=c("#a45371","#e5b6c7","#ebebf7","#89a2d1"),
                       guide = guide_legend(title = "Subway Accessibility Category"), na.value="#D6D6D6") +
  theme_minimal() +
  theme(panel.grid.major = element_line("transparent"),
        axis.text = element_blank()) +
  ggtitle("Subway Deserts \nin NYC")+ 
    theme(panel.grid.major = element_line("transparent"),
          plot.title = element_text(size = 30, face = "bold"),
          legend.title = element_text(size = 12), 
          legend.text = element_text(size = 12)) + 
    guides(shape = guide_legend(override.aes = list(size = 8)),
           color = guide_legend(override.aes = list(size = 8)))
```
`


```{r}
red <- ggplot(nyc_clean) +
  geom_sf(aes(fill = below_poverty_line_count), color = "#8f98aa") +
  scale_fill_gradient(low = "#FCF5EE", high = "#E13728", guide = guide_legend(title = "Number Below \nPoverty Line")) +
  theme_minimal() +
  theme(panel.grid.major = element_line("transparent"),
        axis.text = element_blank()) +
  ggtitle("Impoverishement")+ 
    theme(panel.grid.major = element_line("transparent"),
          plot.title = element_text(size = 26, face = "bold"),
          legend.title = element_text(size = 12), 
          legend.text = element_text(size = 12)) + 
    guides(shape = guide_legend(override.aes = list(size = 8)),
           color = guide_legend(override.aes = list(size = 8)))

yellow <- ggplot(nyc_clean) +
  geom_sf(aes(fill = mean_income), color = "#8f98aa") +
  scale_fill_gradient(low = "#FCF5EE", high = "#F3D24E", guide = guide_legend(title = "Mean Income")) +
  theme_minimal() +
  theme(panel.grid.major = element_line("transparent"),
        axis.text = element_blank()) +
  ggtitle("Mean Income")+
    theme(panel.grid.major = element_line("transparent"),
          plot.title = element_text(size = 26, face = "bold"),
          legend.title = element_text(size = 12),
          legend.text = element_text(size = 12)) +
    guides(shape = guide_legend(override.aes = list(size = 8)),
           color = guide_legend(override.aes = list(size = 8)))

teal <- ggplot(nyc_clean) +
  geom_sf(aes(fill = mean_rent), color = "#8f98aa") +
  scale_fill_gradient(low = "#FCF5EE", high = "#2DBDC7", guide = guide_legend(title = "Dollars")) +
  theme_minimal() +
  theme(panel.grid.major = element_line("transparent"),
        axis.text = element_blank()) +
  ggtitle("Mean Rent")+
    theme(panel.grid.major = element_line("transparent"),
          plot.title = element_text(size = 26, face = "bold"),
          legend.title = element_text(size = 12),
          legend.text = element_text(size = 12)) +
    guides(shape = guide_legend(override.aes = list(size = 8)),
           color = guide_legend(override.aes = list(size = 8)))

purple <- ggplot(nyc_clean) +
  geom_sf(aes(fill = eviction_count), color = "#8f98aa")+
  scale_fill_gradient(low = "#FCF5EE", high = "#7826C0", guide = guide_legend(title = "Number of Evictions")) +
  theme_minimal() +
  theme(panel.grid.major = element_line("transparent"),
        axis.text = element_blank()) +
  ggtitle("Evictions")+ 
    theme(panel.grid.major = element_line("transparent"),
          plot.title = element_text(size = 26, face = "bold"),
          legend.title = element_text(size = 12), 
          legend.text = element_text(size = 12)) + 
    guides(shape = guide_legend(override.aes = list(size = 8)),
           color = guide_legend(override.aes = list(size = 8)))

orange <- ggplot(nyc_clean) +
  geom_sf(aes(fill = unemployment_count), color = "#8f98aa")+
  scale_fill_gradient(low = "#FCF5EE", high = "#FC9228", guide = guide_legend(title = "Number on \nUnemployment")) +
  theme_minimal() +
  theme(panel.grid.major = element_line("transparent"),
        axis.text = element_blank()) +
  ggtitle("Unemployment")+
    theme(panel.grid.major = element_line("transparent"),
          plot.title = element_text(size = 26, face = "bold"),
          legend.title = element_text(size = 12),
          legend.text = element_text(size = 12)) +
    guides(shape = guide_legend(override.aes = list(size = 8)),
           color = guide_legend(override.aes = list(size = 8)))

green <- ggplot(nyc_clean) +
  geom_sf(aes(fill = store_count), color = "#8f98aa")+
  scale_fill_gradient(low = "#FCF5EE", high = "#326902", guide = guide_legend(title = "Number of Stores")) +
  theme_minimal() +
  theme(panel.grid.major = element_line("transparent"),
        axis.text = element_blank()) +
  ggtitle("Retail Food Stores")+ 
    theme(panel.grid.major = element_line("transparent"),
          plot.title = element_text(size = 26, face = "bold"),
          legend.title = element_text(size = 12), 
          legend.text = element_text(size = 12)) + 
    guides(shape = guide_legend(override.aes = list(size = 8)),
           color = guide_legend(override.aes = list(size = 8)))

blue <- ggplot(nyc_clean) +
  geom_sf(aes(fill = school_count), color = "#8f98aa")+
  scale_fill_gradient(low = "#FCF5EE", high = "#5372C4", 
                      guide = guide_legend(title = "Number of Schools")) +
  theme_minimal() +
  theme(panel.grid.major = element_line("transparent"),
        axis.text = element_blank()) +
  ggtitle("Number of Schools")+ 
    theme(panel.grid.major = element_line("transparent"),
          plot.title = element_text(size = 26, face = "bold"),
          legend.title = element_text(size = 12), 
          legend.text = element_text(size = 12)) + 
    guides(shape = guide_legend(override.aes = list(size = 8)),
           color = guide_legend(override.aes = list(size = 8)))

pink <- ggplot(nyc_clean) +
  geom_sf(aes(fill = total_pop), color = "#8f98aa")+
  scale_fill_gradient(low = "#FCF5EE", high = "#F450E1", guide = guide_legend(title = "Number of People")) +
  theme_minimal() +
  theme(panel.grid.major = element_line("transparent"),
        axis.text = element_blank()) +
  ggtitle("Population")+ 
    theme(panel.grid.major = element_line("transparent"),
          plot.title = element_text(size = 26, face = "bold"),
          legend.title = element_text(size = 12), 
          legend.text = element_text(size = 12)) + 
    guides(shape = guide_legend(override.aes = list(size = 8)),
           color = guide_legend(override.aes = list(size = 8)))


brown <- ggplot(nyc_clean) +
  geom_sf(aes(fill = uninsured_count), color = "#8f98aa")+
  scale_fill_gradient(low = "#F8E3DD", high = "#6A4D39", guide = guide_legend(title = "Number of People \n without Insurance Coverage")) +
  theme_minimal() +
  theme(panel.grid.major = element_line("transparent"),
        axis.text = element_blank()) +
  ggtitle("Insurance Coverage")+ 
    theme(panel.grid.major = element_line("transparent"),
          plot.title = element_text(size = 26, face = "bold"),
          legend.title = element_text(size = 12), 
          legend.text = element_text(size = 12)) + 
    guides(shape = guide_legend(override.aes = list(size = 8)),
           color = guide_legend(override.aes = list(size = 8)))
```

```{r}
white <- ggplot(nyc_clean) +
  geom_sf(aes(fill = white_count), color = "#8f98aa") +
  scale_fill_gradient(low = "#FCF5EE", high = "#7B435B", guide = guide_legend(title = "Number White")) +
  theme_minimal() +
  theme(panel.grid.major = element_line("transparent"),
        axis.text = element_blank()) +
  ggtitle("White Population")+ 
    theme(panel.grid.major = element_line("transparent"),
          plot.title = element_text(size = 24, face = "bold"),
          legend.title = element_text(size = 12), 
          legend.text = element_text(size = 12)) + 
    guides(shape = guide_legend(override.aes = list(size = 8)),
           color = guide_legend(override.aes = list(size = 8)))

black <- ggplot(nyc_clean) +
  geom_sf(aes(fill = black_count), color = "#8f98aa") +
  scale_fill_gradient(low = "#FCF5EE", high = "#F25F5C", guide = guide_legend(title = "Number Black")) +
  theme_minimal() +
  theme(panel.grid.major = element_line("transparent"),
        axis.text = element_blank()) +
  ggtitle("Black Population")+ 
    theme(panel.grid.major = element_line("transparent"),
          plot.title = element_text(size = 24, face = "bold"),
          legend.title = element_text(size = 12), 
          legend.text = element_text(size = 12)) + 
    guides(shape = guide_legend(override.aes = list(size = 8)),
           color = guide_legend(override.aes = list(size = 8)))

asian <- ggplot(nyc_clean) +
  geom_sf(aes(fill = asian_count), color = "#8f98aa") +
  scale_fill_gradient(low = "#FCF5EE", high = "#717EC3", guide = guide_legend(title = "Number Asian")) +
  theme_minimal() +
  theme(panel.grid.major = element_line("transparent"),
        axis.text = element_blank()) +
  ggtitle("Asian Population")+ 
    theme(panel.grid.major = element_line("transparent"),
          plot.title = element_text(size = 24, face = "bold"),
          legend.title = element_text(size = 12), 
          legend.text = element_text(size = 12)) + 
    guides(shape = guide_legend(override.aes = list(size = 8)),
           color = guide_legend(override.aes = list(size = 8)))

latinx <- ggplot(nyc_clean) +
  geom_sf(aes(fill = latinx_count), color = "#8f98aa")+
  scale_fill_gradient(low = "#FCF5EE", high = "#FC9A38", guide = guide_legend(title = "Number Latinx")) +
  theme_minimal() +
  theme(panel.grid.major = element_line("transparent"),
        axis.text = element_blank()) +
  ggtitle("Latinx Population")+ 
    theme(panel.grid.major = element_line("transparent"),
          plot.title = element_text(size = 24, face = "bold"),
          legend.title = element_text(size = 12), 
          legend.text = element_text(size = 12)) + 
    guides(shape = guide_legend(override.aes = list(size = 8)),
           color = guide_legend(override.aes = list(size = 8)))
```



## Data Introduction

> All the data used in this project are from two major sources: the Tidycensus package and NYC Open Data. 
> 
> Tidycensus is an R  package interface, developed by Kyle Walker and Matt Herman, that enables easy access to the US Census Bureau’s data APIs and returns Tidyverse-ready data frames from various major US Census Bureau datasets. 
Our demographic and socioeconomic data are drawn from the American Community Survey results found in Tidycensus package. A summary of our ACS data variables is below:
>
- `borough:` Each Neighborhood's Borough.
- `total_pop`: Total Population by Neighborhood
- `mean_income`: Mean Income by Neighborhood
- `below_poverty_line_count`: Number of People Living Below the 100% Poverty Line by Neighborhood
- `mean_rent`:  Mean Rent by Neighborhood
-  `unemployment_count`: Number of People on Unemployment by Neighborhood
-  `latinx_count`: Number of Latinx People by Neighborhood
- `white_count`: Number of White People by Neighborhood
- `black_count`: Number of Black People by Neighborhood
- `native_count`: Number of Native People by Neighborhood
- `asian_count`: Number of Asian People by Neighborhood
- `naturalized_citizen_count`: Number of Naturalized Citizens by Neighborhood
- `noncitizen_count`: Number of Foreign Born People by Neighborhood 
- `uninsured_count`: Number of Uninsured Citizens of any Age by Neighborhood 
> 
> For remaining predictors, we used NYC Open Data's portal to identify specific predictors. In particular, we used geotagged locations of Subway Stops, Bus Stops, Grocery Stores, Schools, and Eviction Sites from the Departments of Transportation, Health, Education, and Housing to calculate neighborhood-specific variables described below: 
>
>
- `school_count`: Number of Public Schools by Neighborhood 
- `eviction_count`: Number of Evictions by Neighborhood 
- `store_count`: Number of Grocery Stores and Food Vendors by Neighborhood 
- `sub_count`: Number of Subway Stations by Neighborhood 
- `bus_count`: Number of Bus Stations by Neighborhood
- `perc_covered_by_transit`: Percent of Neighborhood Within Walking Distance (.25 miles) of Any Subway Stop. 
- `transportation_desert_4cat`: Subway Accessibility by Neighborhood (None, Limited, Satisfactory, Excellent)
>
> Lastly, we acquired subway ridership from Metropolitan Transportation Authority’s turnstile data for the week of September 7, 2019. For each station, entry/exit of each turnstile is recorded. Then, we aggregated this information by taking the station-specific average of subway ridership across the 7 days in the week. Finally, we geotagged each listed station, then took the mean of ridership at all subway stations in each neighborhood to create.
>
- `mean_ridership`: Mean Subway Ridership by Neighborhood for the week of September 7th.



## Data Summaries

> Our data has 224 observations of 26 variables. Below is a preview of our dataset with colnames attached.

```{r eval = TRUE}
library(kableExtra)
kable(head(nyc_clean)) %>% kable_styling() 
```

> Below is a numeric summary of each variable's distribution.

```{r eval = TRUE}
summary(nyc_clean)
  library(table1)
table1(~ total_pop + mean_income + below_poverty_line_count+ 
         mean_rent + unemployment_count + white_count + latinx_count + black_count + 
         native_count + asian_count + uninsured_count + school_count + eviction_count +
         store_count + transportation_desert_4cat+ sub_count + bus_count + mean_ridership + perc_covered_by_transit | borough, data = nyc_clean %>% as.tibble(),  latex_options="HOLD_position") 
```



## Data Visuals

### Non-Spatial {-}

```{r}
library(ggridges)
plot_1<-nyc_clean %>% 
  ggplot(aes(x=mean_income, y=borough, fill=borough), alpha=.6) +
  geom_density_ridges() +
  labs(title="Mean Income", y="")+
    theme(panel.grid.major = element_line("transparent"),
          axis.text.y.left = element_text(size = 16, face = "bold"),
          plot.title = element_text(size = 28,hjust=.5, face = "bold"),
          legend.position="none") +
  scale_fill_manual(values=c("#e09f3e","#16bac5","#717ec3","#5da271"))

plot_2<-nyc_clean %>% 
  ggplot(aes(x=below_poverty_line_count, y=borough, fill=borough), alpha=.6) +
  geom_density_ridges() +
  labs(title="Number Below Poverty Line", y="")+
    theme(panel.grid.major = element_line("transparent"),
          axis.text.y.left = element_text(size = 16, face = "bold"),
          plot.title = element_text(size = 28,hjust=.5, face = "bold"),
          legend.position="none") +
  scale_fill_manual(values=c("#e09f3e","#16bac5","#717ec3","#5da271"))

plot_3<-nyc_clean %>% 
  ggplot(aes(x=mean_rent, y=borough, fill=borough), alpha=.6) +
  geom_density_ridges() +
  labs(title="Mean Rent", y="")+
    theme(panel.grid.major = element_line("transparent"),
          axis.text.y.left = element_text(size = 16, face = "bold"),
          plot.title = element_text(size = 28,hjust=.5, face = "bold"),
          legend.position="none") +
  scale_fill_manual(values=c("#e09f3e","#16bac5","#717ec3","#5da271"))

plot_4<-nyc_clean %>% 
  ggplot(aes(x=unemployment_count, y=borough, fill=borough), alpha=.6) +
  geom_density_ridges() +
  labs(title="Unemployed Counts", y="")+
    theme(panel.grid.major = element_line("transparent"),
          axis.text.y.left = element_text(size = 16, face = "bold"),
          plot.title = element_text(size = 28,hjust=.5, face = "bold"),
          legend.position="none") +
  scale_fill_manual(values=c("#e09f3e","#16bac5","#717ec3","#5da271"))

plot_5<-nyc_clean %>% 
  ggplot(aes(x=white_count, y=borough, fill=borough), alpha=.6) +
  geom_density_ridges() +
  labs(title="White Counts", y="")+
    theme(panel.grid.major = element_line("transparent"),
          axis.text.y.left = element_text(size = 16, face = "bold"),
          plot.title = element_text(size = 28,hjust=.5, face = "bold"),
          legend.position="none") +
  scale_fill_manual(values=c("#e09f3e","#16bac5","#717ec3","#5da271"))

plot_6<-nyc_clean %>% 
  ggplot(aes(x=uninsured_count, y=borough, fill=borough), alpha=.6) +
  geom_density_ridges() +
  labs(title="Uninsured Counts", y="")+
    theme(panel.grid.major = element_line("transparent"),
          axis.text.y.left = element_text(size = 16, face = "bold"),
          plot.title = element_text(size = 28,hjust=.5, face = "bold"),
          legend.position="none") +
  scale_fill_manual(values=c("#e09f3e","#16bac5","#717ec3","#5da271"))


plot_7<-nyc_clean %>% 
  ggplot(aes(x=school_count, y=borough, fill=borough), alpha=.6) +
  geom_density_ridges() +
  labs(title="School Counts", y="")+
    theme(panel.grid.major = element_line("transparent"),
          axis.text.y.left = element_text(size = 16, face = "bold"),
          plot.title = element_text(size = 28,hjust=.5, face = "bold"),
          legend.position="none") +
  scale_fill_manual(values=c("#e09f3e","#16bac5","#717ec3","#5da271"))

plot_8<-nyc_clean %>% 
  ggplot(aes(x=eviction_count, y=borough, fill=borough), alpha=.6) +
  geom_density_ridges() +
  labs(title="Eviction Counts", y="")+
    theme(panel.grid.major = element_line("transparent"),
          axis.text.y.left = element_text(size = 16, face = "bold"),
          plot.title = element_text(size = 28,hjust=.5, face = "bold"),
          legend.position="none") +
  scale_fill_manual(values=c("#e09f3e","#16bac5","#717ec3","#5da271"))

plot_9<-nyc_clean %>% 
  ggplot(aes(x=store_count, y=borough, fill=borough), alpha=.6) +
  geom_density_ridges() +
  labs(title="Food Retail Counts", y="")+
    theme(panel.grid.major = element_line("transparent"),
          axis.text.y.left = element_text(size = 16, face = "bold"),
          plot.title = element_text(size = 28,hjust=.5, face = "bold"),
          legend.position="none") +
  scale_fill_manual(values=c("#e09f3e","#16bac5","#717ec3","#5da271"))

plot_10<-nyc_clean %>% 
  ggplot(aes(x=borough, fill=transportation_desert_4cat), alpha=.6) +
  geom_bar(position="fill") +
  scale_y_continuous(labels = seq(0, 100, by = 25)) +
  labs(title="Subway Accessibility", y="", x="")+
    theme(panel.grid.major = element_line("transparent"),
         # axis.text.y.left = element_blank(),
          axis.text.x.bottom = element_text(size = 16, face = "bold"),
          plot.title = element_text(size = 28,hjust=.5, face = "bold")) +
   scale_fill_manual(values=c("#a45371","#e5b6c7","#ebebf7","#89a2d1"),
                       guide = guide_legend(title = "Subway Accessibility"), na.value="#D6D6D6") 

plot_11<-nyc_clean %>% 
  ggplot(aes(x=sub_count, y=borough, fill=borough), alpha=.6) +
  geom_density_ridges() +
  labs(title="Subway Stop Counts", y="")+
    theme(panel.grid.major = element_line("transparent"),
          axis.text.y.left = element_text(size = 16, face = "bold"),
          plot.title = element_text(size = 28,hjust=.5, face = "bold"),
          legend.position="none") +
  scale_fill_manual(values=c("#e09f3e","#16bac5","#717ec3","#5da271"))


plot_12<-nyc_clean %>% 
  ggplot(aes(x=bus_count, y=borough, fill=borough), alpha=.6) +
  geom_density_ridges() +
  labs(title="Bus Stop Counts", y="")+
    theme(panel.grid.major = element_line("transparent"),
          axis.text.y.left = element_text(size = 16, face = "bold"),
          plot.title = element_text(size = 28,hjust=.5, face = "bold"),
          legend.position="none") +
  scale_fill_manual(values=c("#e09f3e","#16bac5","#717ec3","#5da271"))

plot_13<-nyc_clean %>% 
  ggplot(aes(x=mean_ridership, y=borough, fill=borough), alpha=.6) +
  geom_density_ridges() +
  labs(title="Mean Ridership", y="")+
    theme(panel.grid.major = element_line("transparent"),
          axis.text.y.left = element_text(size = 16, face = "bold"),
          plot.title = element_text(size = 28,hjust=.5, face = "bold"),
          legend.position="none") +
  scale_fill_manual(values=c("#e09f3e","#16bac5","#717ec3","#5da271"))
```

```{r, fig.height=8*4, fig.width=8*4}
library(egg)
ggarrange(plot_1, plot_2, plot_3, 
          plot_4, plot_5, plot_6, 
          plot_7, plot_8, plot_9, 
          plot_10, plot_11, plot_12, 
          plot_13, 
          ncol=4)
```



### Spatial {-}

```{r, fig.height=8*2, fig.width=8*3}
library(egg)
ggarrange(subway_loc, bus_loc, stops, bus_stops, ridership, access, ncol=3)
```

```{r, fig.height=8*3, fig.width=8*3}
ggarrange(red, orange, yellow, green, teal, blue, purple, pink, brown, ncol=3)
```

```{r, fig.height=16, fig.width=16}
ggarrange(white, black, latinx, asian, ncol=2)
```

## Model Building

### Models 1 & 2: Non-Hierarchical Grouping

#### Poisson {-}

$$\begin{split}
\text{White}_{i} \mid  \beta_{0}, \beta_1, ..., \beta_k & \sim \text{Pois}(\lambda_{i}) \; \; \; \; \text{where} \log(\lambda_{i}) = \beta_{0} + \sum^{10}_{k=1}X_{ik}\beta_k \\
\beta_{0c}  &\sim N(0,1) \\
\beta_{1} & \sim ~ N(0, 0.00013^2) \\				
\beta_{2} & \sim ~ N(0, 0.000073^2) \\				
\beta_{3} & \sim ~ N(0, 0.0053^2) \\				
\beta_{4} & \sim ~ N(0, 0.0029^2) \\				
\beta_{5} & \sim ~ N(0, 5.281^2) \\				
\beta_{6} & \sim ~ N(0, 5.375^2) \\				
\beta_{7} & \sim ~ N(0, 6.719^2) \\				
\beta_{8} & \sim ~ N(0, 0.3905^2) \\				
\beta_{9} & \sim ~ N(0,0.0717^2) \\				
\beta_{10} & \sim ~ N(0, 0.063^2) \\
\end{split}$$

```{r}
poisson_non_hierarchical <- stan_glm(
  white_count ~ mean_income + mean_rent + 
    unemployment_count + sub_count + 
    transportation_desert_4cat + school_count + 
    store_count + bus_count + 
    eviction_count + uninsured_count,
  data = nyc_clean,
  family = poisson,
  chains = 2, iter = 100*2, seed = 84735, refresh = 0
)
```

```{r, fig.width=12, fig.height=6}
pp_check(poisson_non_hierarchical) + 
  xlab("White Resident Count") +
  labs(title = "Poisson")+
  theme(plot.title =  element_text(face="bold", size=25, hjust=.5)) 

library(kableExtra)

tidy(poisson_non_hierarchical, effects = "fixed", conf.int = TRUE, conf.level = 0.95) %>% 
  
  mutate(estimate= ifelse(term == "(Intercept)", exp(estimate), (exp(estimate)-1)*100), 
         conf.low= ifelse(term == "(Intercept)", exp(conf.low), (exp(conf.low)-1)*100), 
         conf.high = ifelse(term == "(Intercept)", exp(conf.high), (exp(conf.high)-1)*100))%>%
  filter(conf.low	> 0 & conf.high > 0 | conf.low	< 0 & conf.high < 0) %>%
  kable(align = "c", caption = "Non-Hierarchical Poisson - Model Summary") %>% 
  kable_styling()


nyc_predict_clean <- nyc_clean %>%
  na.omit()
set.seed(84735)

predictions_poisson <-  posterior_predict(
  poisson_non_hierarchical, newdata = nyc_predict_clean)

library(tidybayes)
library(bayesplot)

ppc_intervals(nyc_predict_clean$white_count, yrep = predictions_poisson,
              prob_outer = 0.95) +
  ggplot2::scale_x_continuous(
    labels = nyc_predict_clean$nta_id,
    breaks = 1:nrow(nyc_predict_clean)) +
  xaxis_text(angle = 90, hjust = 1) +
  theme_linedraw()+
  theme(panel.grid.major = element_line("transparent"),
        axis.title.y = element_blank(),
        axis.text.y = element_blank())+
  coord_flip() 
```

#### Negative Binomial {-}

$$\begin{split}
\text{White}_{ij} \mid  \beta_{0j}, \beta_1, ..., \beta_k, \sigma_y & \sim \text{NegBin}(\mu_{ij}, r) \; \; \; \; \text{where} \log(\lambda_{i}) = \beta_{0} + \sum^{10}_{k=1}X_{ik}\beta_k \\
\beta_{0c}  &\sim N(0,1) \\
\beta_{1} & \sim ~ N(0, 0.00013^2) \\				
\beta_{2} & \sim ~ N(0, 0.000073^2) \\				
\beta_{3} & \sim ~ N(0, 0.0053^2) \\				
\beta_{4} & \sim ~ N(0, 0.0029^2) \\				
\beta_{5} & \sim ~ N(0, 5.281^2) \\				
\beta_{6} & \sim ~ N(0, 5.375^2) \\				
\beta_{7} & \sim ~ N(0, 6.719^2) \\				
\beta_{8} & \sim ~ N(0, 0.3905^2) \\				
\beta_{9} & \sim ~ N(0,0.0717^2) \\				
\beta_{10} & \sim ~ N(0, 0.063^2) \\
\end{split}$$

```{r, cache=TRUE}
negbin_non_hierarchical <- stan_glm(
  white_count ~  mean_income + mean_rent + 
    unemployment_count + sub_count + 
    transportation_desert_4cat + school_count + 
    store_count + bus_count + 
    eviction_count + uninsured_count,
  data = nyc_clean,
  family = neg_binomial_2,
  chains = 2, iter = 100*2, seed = 84735, refresh = 0
)
  
```

```{r, fig.width=12, fig.height=6}
pp_check(negbin_non_hierarchical) + 
  xlab("White Resident Count") +
  xlim(0,100000)+
  labs(title = "Negative Binomial")+
  theme(plot.title =  element_text(face="bold", size=25, hjust=.5)) 

tidy(negbin_non_hierarchical, effects = "fixed", conf.int = TRUE, conf.level = 0.95)%>% 
  
  mutate(estimate= ifelse(term == "(Intercept)", exp(estimate), (exp(estimate)-1)*100), 
         conf.low= ifelse(term == "(Intercept)", exp(conf.low), (exp(conf.low)-1)*100), 
         conf.high = ifelse(term == "(Intercept)", exp(conf.high), (exp(conf.high)-1)*100))%>%
  filter(conf.low	> 0 & conf.high > 0 | conf.low	< 0 & conf.high < 0) %>%
  kable(align = "c", caption = "Non-Hierarchichal Negative Binomial - Model Summary") %>% 
  kable_styling()

nyc_predict_clean <- nyc_clean %>%
  na.omit()
set.seed(84735)

predictions_negbin <-  posterior_predict(
  negbin_non_hierarchical, newdata = nyc_predict_clean)

ppc_intervals(nyc_predict_clean$white_count, yrep = predictions_negbin,
              prob_outer = 0.95) +
  ggplot2::scale_x_continuous(
    labels = nyc_predict_clean$nta_id,
    breaks = 1:nrow(nyc_predict_clean)) +
	xaxis_text(angle = 90,  hjust = 1) +
  theme_linedraw()+
  theme(panel.grid.major = element_line("transparent"),
        axis.title.y = element_blank(),
        axis.text.y = element_blank())+
  coord_flip()
```


### Models 2 & 3: Hierarchy by Borough

#### Poisson {-}

$$\begin{split}
\text{White}_{ij} \mid  \beta_{0j}, \beta_1, ..., \beta_k, \sigma_y & \sim \text{Pois}(\lambda_{ij}) \\
& \text{where} \log(\lambda_{ij}) = \beta_{0j} + \sum^{11}_{k=1}X_{ijk}\beta_k \\
\beta_{0j} \mid \beta_0, \sigma_0 & \stackrel{ind}{\sim} N(\beta_0, \sigma_0^2)\\
\beta_{0c}, \beta_k & \stackrel{ind}{\sim} N(0,1) \\
\sigma_y, \sigma_0 & \stackrel{ind}{\sim} Exp(1)
\end{split}$$

```{r}
poisson_hierarchical <- stan_glmer(
 white_count ~ mean_income + mean_rent + 
    unemployment_count + sub_count + 
    transportation_desert_4cat + school_count + 
    store_count + bus_count + 
    eviction_count + uninsured_count + (1 | borough),
  data = nyc_clean,
  family = poisson,
  chains = 2, iter = 100*2, seed = 84735, refresh = 0
)
```

```{r, fig.width=12, fig.height=6}
pp_check(poisson_hierarchical) + 
  xlab("White Resident Count") +
  labs(title = "Poisson")+
  theme(plot.title =  element_text(face="bold", size=25, hjust=.5)) 

library(kableExtra)

tidy(poisson_hierarchical, effects = "fixed", conf.int = TRUE, conf.level = 0.95) %>% 
  
  mutate(estimate= ifelse(term == "(Intercept)", exp(estimate), (exp(estimate)-1)*100), 
         conf.low= ifelse(term == "(Intercept)", exp(conf.low), (exp(conf.low)-1)*100), 
         conf.high = ifelse(term == "(Intercept)", exp(conf.high), (exp(conf.high)-1)*100))%>%
  filter(conf.low	> 0 & conf.high > 0 | conf.low	< 0 & conf.high < 0) %>%
  kable(align = "c", caption = "Hierarchicahl Poisson - Model Summary") %>% 
  kable_styling()


nyc_predict_clean <- nyc_clean %>%
  na.omit()
set.seed(84735)

predictions_poisson <-  posterior_predict(
  poisson_hierarchical, newdata = nyc_predict_clean)

library(tidybayes)
library(bayesplot)

ppc_intervals(nyc_predict_clean$white_count, yrep = predictions_poisson,
              prob_outer = 0.95) +
  ggplot2::scale_x_continuous(
    labels = nyc_predict_clean$nta_id,
    breaks = 1:nrow(nyc_predict_clean)) +
  xaxis_text(angle = 90, hjust = 1) +
  theme_linedraw()+
  theme(panel.grid.major = element_line("transparent"),
        axis.title.y = element_blank(),
        axis.text.y = element_blank())+
  coord_flip() 
```

#### Negative Binomial {-}

$$\begin{split}
\text{White}_{ij} \mid  \beta_{0j}, \beta_1, ..., \beta_k, \sigma_y & \sim \text{NegBin}(\mu_{ij}, r) \\
& \text{where} \log(\mu_{ij}) = \beta_{0j} + \sum^{11}_{k=1}X_{ijk}\beta_k \\
\beta_{0j} \mid \beta_0, \sigma_0 & \stackrel{ind}{\sim} N(\beta_0, \sigma_0^2)\\
\beta_{0c}, \beta_k & \stackrel{ind}{\sim} N(0,1) \\
\sigma_y, \sigma_0 & \stackrel{ind}{\sim} Exp(1)
\end{split}$$

```{r,  cache=TRUE}
negbin_hierarchical <- stan_glmer(
 white_count ~ mean_income + mean_rent + 
    unemployment_count + sub_count + 
    transportation_desert_4cat + school_count + 
    store_count + bus_count + 
    eviction_count + uninsured_count + (1 | borough),
  data = nyc_clean,
  family = neg_binomial_2,
  chains = 2, iter = 100*2, seed = 84735, refresh = 0)
```

```{r, fig.width=12, fig.height=6}
pp_check(negbin_hierarchical) + 
  xlab("White Resident Count") +
  labs(title = "Negative Binomial")+
  theme(plot.title =  element_text(face="bold", size=25, hjust=.5)) 

tidy(negbin_hierarchical, effects = "fixed", conf.int = TRUE, conf.level = 0.95)%>% 
  
  mutate(estimate= ifelse(term == "(Intercept)", exp(estimate), (exp(estimate)-1)*100), 
         conf.low= ifelse(term == "(Intercept)", exp(conf.low), (exp(conf.low)-1)*100), 
         conf.high = ifelse(term == "(Intercept)", exp(conf.high), (exp(conf.high)-1)*100))%>%
  filter(conf.low	> 0 & conf.high > 0 | conf.low	< 0 & conf.high < 0) %>%
  kable(align = "c", caption = "Hierarchichal Negative Binomial - Model Summary") %>% 
  kable_styling()

nyc_predict_clean <- nyc_clean %>%
  na.omit()
set.seed(84735)

predictions_negbin <-  posterior_predict(
  negbin_hierarchical, newdata = nyc_predict_clean)

ppc_intervals(nyc_predict_clean$white_count, yrep = predictions_negbin,
              prob_outer = 0.95) +
  ggplot2::scale_x_continuous(
    labels = nyc_predict_clean$nta_id,
    breaks = 1:nrow(nyc_predict_clean)) +
	xaxis_text(angle = 90,  hjust = 1) +
  theme_linedraw()+
  theme(panel.grid.major = element_line("transparent"),
        axis.title.y = element_blank(),
        axis.text.y = element_blank())+
  coord_flip()
```


## Next Steps

> We intend to adjust our model specifications and reconsider the construction and inclusion of our predictors. For example, we may want to rethink how we're making our transit-access variable, whether including car ownership or transit use, and what predictors we're specifically using in our models.
>
> Moving forward, we want to build some non-hierarchical models predicting subway and bus count using the demographic data (like median income, rent, percentage white population, etc) to see the flip-side of what we are looking at right now with our models above. 
>
> Our current "hierarchical models" attempt to capture a spatial interaction, but are not properly set up. So, we will include latitude and longitude variables into our model to account for spatial relationships and perhaps do away with hierarchy. However, we may introduce a borough-wide level of grouping or use `CARBayes` to adjust for the spatial factors.


## Participation

>
- **Sam Ding**: Pulled and prepared subway ridership and access data, then harmonized transit data with existing neighborhood data. 
- **Vichy Meas**: Helped clean both transit and demographic data, scaffolded the checkpoint 3 responses, and helped plan out transit questions. 
- **Freddy Barragan**: Pulled and prepared grocery, bus stop, school, eviction, and census data, made exploratory visualizations by neighborhood, built/coded our proposed demographic models.
- **Juthi Dewan**: Harmonized, cleaned, and joined all disparate datasets, prepared our data summaries, built/coded our proposed demographic models.


